A Generalized Sphere Theorem for\\Positively Curved Combinatorial 3-Manifolds

### 2013-06-27 paper/paper.tex
added link to github material in bibliography and referenced it in paper

Python programs (available on request) were written to examine each manifold in the census and compute its diameter and edge-diameter. See Figure \ref{fig:type_statistics} for a plot of the number of manifolds by topological type and diameter. As claimed, every manifold with diameter greater than $J$ is a 3-sphere. The corresponding data using the coarser-grained edge-diameter can be found in Figure \ref{fig:type_statistics_edges}. Note the existence of $3$-manifolds with edge-diameter greater than half the maximum allowed edge-diameter and which are {\em not} homeomorphic to the 3-sphere.

@@

% \input{bigtable.tex}

>>>>

Python programs were written to examine each manifold in the census and compute its diameter and edge-diameter. Code is available online \cite{Gintautas_Trout_github_manifold} along with a complete table of results for each manifold. See Figure \ref{fig:type_statistics} for a plot of the number of manifolds by topological type and diameter. As claimed, every manifold with diameter greater than $J$ is a 3-sphere. The corresponding data using the coarser-grained edge-diameter can be found in Figure \ref{fig:type_statistics_edges}. Note the existence of $3$-manifolds with edge-diameter greater than half the maximum allowed edge-diameter and which are {\em not} homeomorphic to the 3-sphere.

@@
